### 2024-04-15 introduction.tex
new

Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
For financial products like option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model tail risk with a rule-based design.
In this thesis, we focus on building and analyzing nested simulation procedures for risk management applications of financial derivatives and insurance products.

>>>>

Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
For financial products like option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model tail risk with a rule-based design.
In this thesis, we focus on building and analyzing nested simulation procedures for risk management applications of financial derivatives and insurance products.
Nested simulation, also known as nested stochastic modeling and stochastic-on-stochastic modeling, becomes necessary when stochastic simulation of a parameter of interest is contingent on another quantity to be determined stochastically.
In the context of financial engineering, nested simulation is used to model the risk of a financial product whose payoff depends on a set of underlying risk factors.
A nested simulation procedure consists of two levels of simulation: the outer level simulates the underlying risk factors, while the inner level estimates the conditional mean of the payoff for a given risk factor with another Monte Carlo simulation.
